\documentclass{article}
\usepackage{amsmath,amssymb,amsthm,latexsym,paralist}
\usepackage{tikz}

\theoremstyle{definition}
\newtheorem{problem}{Problem}
\newtheorem*{solution}{Solution}
\newtheorem*{resources}{Resources}

\newcommand{\name}[1]{\noindent\textbf{Name: #1}}
\newcommand{\honor}{\noindent On my honor, as an Aggie, I have neither
  given nor received any unauthorized aid on any portion of the
  academic work included in this assignment. Furthermore, I have
  disclosed all resources (people, books, web sites, etc.) that have
  been used to prepare this homework. \\[1ex]
 \textbf{Signature:} Anthony Bibbo }

 \newcommand{\checklist}{\noindent\textbf{Checklist:}
\begin{compactitem}[$\Box$] 
\item Did you add your name? 
\item Did you disclose all resources that you have used? \\
(This includes all people, books, websites, etc. that you have consulted)
\item Did you sign that you followed the Aggie honor code? 
\item Did you solve all problems? 
\item Did you typeset your answers entirely in LaTeX? 
\item Did you submit the pdf file of your homework?
\end{compactitem}
}



\newcommand{\problemset}[1]{\begin{center}\textbf{Problem Set
      #1}\end{center}}
\newcommand{\duedate}[2]{\begin{quote}\textbf{Due dates:} Electronic
    submission of the pdf file of this homework is due on
    \textbf{#1} on canvas. The homework must be typeset with LaTeX to
    receive any credit. All answers must be formulated in your own words.\end{quote} }

\newcommand{\N}{\mathbf{N}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\Z}{\mathbf{Z}}


\begin{document}
\problemset{7}
\duedate{10/24/2025 before 11:59pm}

\textbf{Watch out for additional material that will appear on
  Thursday! Deadline is on Friday, as usual.} 

\name{ Anthony Bibbo}
\begin{resources} Course Textbook, Lecture notes, Lecture slides, Perusall
\end{resources}
\honor


\newpage


Read the chapters on ``Elementary Graph Algorithms'' and
``Single-Source Shortest Paths'' in our textbook before
attempting to answer these questions.

\begin{problem}[20 points]
Give an algorithm that determines whether or not a given undirected
graph $G=(V,E)$ contains a cycle. Your algorithm should run in $O(V)$
time, independent of the number $|E|$ of edges. 
\end{problem}
\begin{solution}
\end{solution}

\begin{problem}[20 points]
Given a weighted, directed graph $G=(V,E)$ with no negative-weight
cycles, let $m$ be the maximum over all vertices $v\in V$ of the minimum
number of edges in a shortest path from the source $s$ to $v$. (Here, the
shortest path is by weight, not the number of edges.) Suggest a simple
change to the Bellman-Ford algorithm that allows it to terminate in $m+1$
passes, even if $m$ is not known in advance.
\end{problem}
\begin{solution}
\end{solution}

\begin{problem}[20 points]
Suppose that we change line 6 of Dijkstra’s algorithm in our textbook
to the following.\\[1ex]
6 \textbf{while} $|Q| > 1$ \\[1ex] 
This change causes the while loop to execute $|V|-1$ times instead of
$|V |$ times. Is this proposed algorithm correct? Explain. 
[Use the version of Dijkstra's algorithm from the textbook]
\end{problem}
\begin{solution}
\end{solution}

\begin{problem}[40 points]
  Help Professor Charlie Eppes find the most likely escape routes of
  thieves that robbed a bookstore on Texas Avenue in College
  Station. The map will be published on Thursday evening. In
  preparation, you might want to implement Dijkstra's single-source
  shortest path algorithm, so that you can join the manhunt on
  Thursday evening. Include your implementation of
  Dijkstra's algorithm and explain all details of your choice of the
  min-priority queue.

  [Edge weight 1 means very desirable street, weight
  2 means less desirable street]

  
\end{problem}
\begin{solution}
\end{solution}


Make sure that you derive the solutions to this homework by yourself
without any outside help. Searching for solutions on the internet or
asking any form of AI is not allowed. Write the solutions in your own
words. Use version control for your program development and be
prepared to show and explain any version of your code. 


\medskip



\goodbreak
\checklist
\end{document}
